Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-14 documents/BrazilSlides/slides.tex
Added some plots that depict the typical behaviour of super-Fritz violations.

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks IIP, Nov. 2016}

@@

\begin{frame}
    \frametitle{Table of Contents}
\tableofcontents

\section{Tools}

@@

\begin{frame}
    \frametitle{Graph Theory [Optional Slide]}
    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
    \begin{itemize}
        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
    \end{itemize}
    Notation extends to sets of nodes $N \subseteq \nodes$,
    \begin{itemize}
        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
    \end{itemize}
    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
\end{frame}

@@

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \begin{itemize}
            \item $\# \text{Columns} = 4^{12} = 16,777,216$
            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
            \item $\# \text{Non-zero Entries} = 201,326,592$
        \end{itemize}
    \end{itemize}
\end{frame}

@@

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels
        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Incidence}
\end{frame}

@@

\section{Searching for New Distributions}
\begin{frame}
    \frametitle{Numerical Optimization}
\end{frame}

@@

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = 1 \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing States Cont'd}
    \begin{itemize}
        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
        \item Freedom to choice $k$
        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \item $d^2 - \br{d-k}^2 - k + \br{k-1} = 2dk -k^2 -1$ real-valued parameters (no-degeneracy)
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $2dn -n^2 -1$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
            \item Shifts one qubit to the left
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]

@@

\begin{frame}
    \frametitle{Maximally Violating Distributions}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item New causal compatibility inequalities have been found for the TS
        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
        \item Proof of non-classicality is robust to noise
        \item Fritz witnessable by party symmetric inequalities
        \item Maximally violating distributions are different than Fritz but also similar
        \item Further research is necessary
    \end{itemize}
\end{frame}

>>>>

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1,2}}
\institute
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada \\
    \inst{2}%
    University of Waterloo\\
    Ontario, Canada \\
}
\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}

@@

% \begin{frame}
%     \frametitle{Table of Contents}
% \tableofcontents

% \end{frame}

@@

\begin{frame}
    \frametitle{Graph Theory [Optional]}
    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
    \begin{itemize}
        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
    \end{itemize}
    Notation extends to sets of nodes $N \subseteq \nodes$,
    \begin{itemize}
        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
    \end{itemize}
    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
\end{frame}

@@

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
        \begin{itemize}
            \item $\# \text{Columns} = 4^{12} = 16,777,216$
            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
            \item $\# \text{Non-zero Entries} = 201,326,592$
        \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
\end{frame}

\begin{frame}
    \frametitle{Causal Symmetry and Inflation}
    \begin{itemize}
        \item Causal symmetry group for $\graph'$ is no good!
        \item Not possible to deflate inequality if it's not in terms of injectable sets
        \begin{definition}
            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
        \end{definition}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Restricted Causal Symmetry of Large Inflation}
    \begin{itemize}
        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
    \end{itemize}
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\gep_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Incidence}
    \begin{itemize}
        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
    \end{itemize}
    \begin{align*}
        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
    \end{align*}
    \begin{itemize}
        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
    \end{itemize}
    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
    \begin{itemize}
        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
        \item For large inflation $M$ is $16,896 \times 16,777,216$
        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
    \end{itemize}
\end{frame}

@@

@@

\begin{frame}
    \frametitle{Numerical Optimization}
    \begin{itemize}
        \item Attempt to find new non-classical distributions
        \item Objective function $f\br{\la} \in \R$
        \begin{enumerate}
            \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
            \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
            \item Distribution $\prob[ABC]$
            \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
            \item Output is objective value $I\br{\prob[ABC]}$
        \end{enumerate}
        \item Numerical minimization of $f\br{\la}$
        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
        \item Non-convex, non-linear, smooth/continuous
        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
        \item Stochastic methods: simulated annealing, basin-hopping
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing States Cont'd}
    \begin{itemize}
        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
        \item Freedom to choice $k$
        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
            \item Shifts one qubit to the left
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
\end{frame}

\begin{frame}
    \frametitle{Results}
    \begin{itemize}
        \item Full rank $\rho, M$ gives $81$ free parameters
        \[ \abs{\la} = 3 \cdot (12 + 3) + 3 \cdot 12 = 81 \]
        \item Parameterization of quantum distributions still degenerate
        \item Noisy seed (Gaussian noise):
        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
        \item Uniform seed:
        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
    \end{itemize}

@@

\begin{frame}
    \frametitle{Fritz Local Minima}
    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
\end{frame}

\begin{frame}
    \frametitle{Fritz Local Minima Zoomed}
    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed_Zoomed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Maximally Violating Distributions}
    \begin{itemize}
        \item Able to out-perform violation provided by Fritz distribution
        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
        \item Violation very sensitive to the initial parameters $\la_{(0)}$
        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item New causal compatibility inequalities have been found for the TS
        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
        \item Proof of non-classicality is robust to noise
        \item Fritz witness-able by party symmetric inequalities
        \item Maximally violating distributions are different than Fritz but also similar
        \item Further research is necessary
    \end{itemize}
\end{frame}
